Supplementary Material for Food-web complexity alters the fitness landscape of an insect herbivore

### 2018-06-21 supp_mat_complexity_selection.Rmd
updated .Rmd to cache chunks so I don't have to rerun code that is unchanged.

```{r AIC Model Selection}

@@

Now let's compare the best GAMMs to analog generalized linear mixed-models (GLMM). If these GLMMs have a lower AIC value than their respective GAMMs, then this suggests that there is only evidence of directional selection in our data.
```{r}
# Note that I still use gamm.model to allow for appropriate model comparisons

@@

```{r Selection Gradients - Complex Food Web}
# note that I've switched to using the lme4 package to analyzing the GLMM

@@

```{r Selection Gradients - Simple Food Web}

@@

To ensure we are calculating these selection gradients correctly, we'll compare our results to those obtained from the *gsg* package developed by Michael Morrissey.
```{r Check Gradient Calculations}

@@

```{r gsg Comparison}

@@

```{r Compare Selection Gradients across Treatments - GLMM}

@@

```{r Compare Selection Gradients across Treatments - gsg GAMM}

@@

```{r Univariate Fitness Landscapes}
## Gall size ----

@@

```{r Multivariate Landscapes}

@@

Now we plot the fitness landscapes associated with different combinations of gall phenotypes. We restrict these plots to 1 SD above and below the mean trait value, as this contains the majority of phenotypes under selection. Therefore, this fitness landscape integrates information from the fitness function with information about distributions of phenotype, and has been suggested to be a more informative way to visualize the magnitude of natural selection.
```{r Fitness Landscapes}

>>>>

```{r AIC Model Selection, cache=TRUE}

@@

Now let's compare the best GAMMs to analog generalized linear mixed-models (GLMM). If these GLMMs have a lower AIC value than their respective GAMMs, then this suggests that there is only evidence of directional selection in our data.
```{r GAMM vs GLMM, cache=TRUE}
# Note that I still use gamm.model to allow for appropriate model comparisons

@@

```{r Selection Gradients - Complex Food Web, cache=TRUE}
# note that I've switched to using the lme4 package to analyzing the GLMM

@@

```{r Selection Gradients - Simple Food Web, cache=TRUE}

@@

To ensure we are calculating these selection gradients correctly, we'll compare our results to those obtained from the *gsg* package developed by Michael Morrissey.
```{r Check Gradient Calculations, cache=TRUE}

@@

```{r gsg Comparison, cache=TRUE}

@@

```{r Compare Selection Gradients across Treatments - GLMM, cache=TRUE}

@@

```{r Compare Selection Gradients across Treatments - gsg GAMM, cache=TRUE}

@@

```{r Univariate Fitness Landscapes, cache=TRUE}
## Gall size ----

@@

```{r Multivariate Landscapes, cache=TRUE}

@@

Now we plot the fitness landscapes associated with different combinations of gall phenotypes. We restrict these plots to 1 SD above and below the mean trait value, as this contains the majority of phenotypes under selection. Therefore, this fitness landscape integrates information from the fitness function with information about distributions of phenotype, and has been suggested to be a more informative way to visualize the magnitude of natural selection.
```{r Fitness Landscapes, eval=FALSE}
